The Weakly Nonlinear Magnetorotational Instability in a local geometry

### 2017-03-03 paper/thingap_ref_response/thingap_mri_paper_ref_response_apj.tex
new title, a little more in new section

\title{The Weakly Nonlinear Magnetorotational Instability in a thin-gap Taylor-Couette flow}

@@

The nonlinear property of primary MRI modes in the shearing box motivates the addition of radial boundaries, such that the nonlinear evolution of the weakly nonlinear MRI can be properly considered. It also begs the question of whether some additional nonlinear mechanism can be introduced such that the fastest-growing modes are no longer nonlinear solutions to the shearing box equations. It has already been shown that the Hall effect does not negate the nonlinear property of primary MRI modes \citep{Kunz:2013}. However, it seems to have been overlooked in the literature that these linear modes are \textit{not} solutions of the nonlinear ambipolar diffusion term, which takes the form

@@

The Ginzburg-Landau form of the amplitude equation can be found in any system with Euclidean symmetry and a quadratic maximum in growth rate with respect to the wavenumber \citep{Hoyle:2006}. In this case, the Euclidean symmetry comes from axisymmetry in the $x$-$z$ plane, and the quadratic maximum is a consequence of the linear dispersion relation given in Appendix~\ref{app:dispersion}. In Paper II, we show that the same symmetry occurs in the axisymmetric global geometry as well.
The Ginzburg-Landau equation arises due to symmetries in the local MRI equations, irrespective of the boundary conditions to which they are subjected. This means that the local MRI is able to saturate via nonlinear mode interaction so long as the primary MRI modes are not exact solutions of the nonlinear terms. This can be achieved by considering the effects of ambipolar diffusion when the boundary conditions are shear periodic, or by enforcing wall-like radial boundary conditions. Both constructions require the most unstable mode to have nonconstant radial structure. %So long as our system permits the most unstable mode to nonlinearly interact with

>>>>

%\title{The Weakly Nonlinear Magnetorotational Instability in a thin-gap Taylor-Couette flow}
\title{The Weakly Nonlinear Magnetorotational Instability in a local geometry}

@@

The nonlinear property of primary MRI modes in the shearing box motivates the addition of radial boundaries, such that the nonlinear evolution of the weakly nonlinear MRI can be properly considered. It also begs the question of whether some additional nonlinear mechanism can be introduced such that the fastest-growing modes are no longer nonlinear solutions to the shearing box equations. It has already been shown that the Hall effect does not negate the nonlinear property of primary MRI modes \citep{Kunz:2013}. However, it seems to have been overlooked in the literature that these linear modes are \textit{not} solutions of the nonlinear ambipolar diffusion term, which is proportional to

@@

The Ginzburg-Landau form of the amplitude equation can be found in any system with Euclidean symmetry and a quadratic maximum in growth rate with respect to the wavenumber \citep{Hoyle:2006}. In this case, the Euclidean symmetry comes from axisymmetry in the $x$-$z$ plane, and the quadratic maximum is a consequence of the linear dispersion relation given in Appendix~\ref{app:dispersion}. In Paper II, we show that the same symmetry occurs in the axisymmetric global geometry as well.
The Ginzburg-Landau equation arises due to symmetries in the local MRI equations, irrespective of the boundary conditions to which they are subjected. This means that the local MRI is able to saturate via nonlinear mode interaction so long as the primary MRI modes are not exact solutions of the nonlinear terms. This can be achieved by considering the effects of ambipolar diffusion when the boundary conditions are shear periodic, or by enforcing wall-like radial boundary conditions. Both constructions require the most unstable mode to have nonconstant radial structure. Physically, this radial variation impedes the free exchange of angular momentum facilitated by the uniform stretching of channel modes.  %So long as our system permits the most unstable mode to nonlinearly interact with
